### 2021-09-13 presentation/presentation.tex
update paper presentation

\begin{frame}[plain]
  \titlepage%
  \note{15 minutes !!!!\\}
  \script{Hello, I'm Rafael Accácio and on behalf of my co Authors Romain Bourdais and Hervé Guéguen I'm here to present our paper for the SysTol'21 called «Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation».\\}
  \script{This presentation is available at the address shown or by flashing the QR code.\\}
\end{frame}

>>>>

\begin{frame}[plain]
  \titlepage%
  \note{15 minutes !!!!\\}
  \script{Hello, I'm Rafael Accácio and on behalf of my colleagues Romain Bourdais and Hervé Guéguen I'm here to present our paper for the SysTol'21 called «Detection and Mitigation of Corrupted Information in Distributed Model Predictive Control Based on Resource Allocation».\\}
  \script{This presentation is available at the address shown or by flashing the QR code.\\}
\end{frame}
